Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-06-30 doc/manuscript/manuscript.Rmd
update table 1 in manuscript

USA       CO     eat               2007, 2010 Yellow                       13

                 gree              2007, 2010 Pinto, Yellow                14

@@

@@

USA       MI     eln                     2009 unk                           1

@@

@@

                 wmn        2003, 2004, 2005, 11A, 37, 38, B07104,         43 
                                   2008, 2009 Beryl, Bunsi, cornell,          
                                              G122, Orion, PO7863, WM31

@@

USA       ND     gfc               2007, 2010 unk                           9

@@

                 rrv                     2007 unk                          21

USA       NE     mtc               2007, 2010 Beryl, Emerson, Orion        12

@@

                 wmn        2004, 2005, 2008, Beryl, Bunsi, G122,          27 
                                         2010 PO7683, unk

@@

USA       OR     corv                    2003 G122                          1

@@

                 wmn               2003, 2004 Beryl, Bunsi, G122           15

USA       WA     prsr                    2007 Merlot, Pinto, redkid        22

@@

                 wmn        2003, 2004, 2005, 11A, 37, 38, Beryl, Bunsi,   36 
                                         2008 cornell, G122, Orion,           
                                              PO7104, PO7863, WM31

@@

Mexico           wmn                     2005 Beryl, Bunsi, G122           18

France           flds                    2012 unk                           4

                 wmn               2004, 2005 Beryl, Bunsi, G122           18

Australia        vic                     2004 Beryl                         2

                 wmn                     2004 Beryl, Bunsi, G122            4

>>>>

USA       CO     gree              2007, 2010 Pinto, Yellow                14

@@

                 eat               2007, 2010 Yellow                       13

@@

USA       MI     wmn        2003, 2004, 2005, 11A, 37, 38, B07104,         43 
                                   2008, 2009 Beryl, Bunsi, cornell,          
                                              G122, ion, PO7863, WM31

@@

                 eln                     2009 unk                           1

@@

@@

USA       ND     rrv                     2007 unk                          21

                 gfc               2007, 2010 unk                           9

@@

USA       NE     wmn        2004, 2005, 2008, Beryl, Bunsi, G122,          27 
                                         2010 PO7683, unk

                 mtc               2007, 2010 Beryl, Emerson, Orion        12

@@

@@

USA       OR     wmn               2003, 2004 Beryl, Bunsi, G122           15

                 corv                    2003 G122                          1

@@

USA       WA     wmn        2003, 2004, 2005, 11A, 37, 38, Beryl, Bunsi,   36 
                                         2008  cornell, G122, Orion,          
                                              PO7104, PO7863, WM31

                 prsr                    2007 Merlot, Pinto, redkid        22

@@

@@

Mexico    -      wmn                     2005 Beryl, Bunsi, G122           18

France    -      wmn               2004, 2005 Beryl, Bunsi, G122           18

                 flds                    2012 unk                           4

Australia -      wmn                     2004 Beryl, Bunsi, G122            4

                 vic                     2004 Beryl                         2
